\SectionHeading{Experience}

\NewEntry{Broadway Technology}{Senior Software Consultant}{New York, NY}{July 2018 -- Present}
\Description{
\begin{itemize}
    \item Designing, building, and deploying mission-critical fintech solutions to satisfy complex client requirements.
    \item Implemented various enhancements and bug fixes to graph-based matchine engine, which allows complex matches between diverse order types and outright and synthetic financial instruments. Leveraged heuristics to manage graph-search complexity.
    \item Designed and implemented loan management service for cryptocurrency trading platform. The service manages loan bookkeeping and provides an API to request loans, confirm loans, transfer funds between accounts.
    \item Implemented margin trading flow across multiple distributed components, which allowed a brokerage firm to offer out margin risk trading capabilities in cryptocurrency trading. Created risk controls to prevent users from breaching their risk limits, protecting the brokerage firm from overexposure.
    \item Provided developer support for clients integrating to Broadway's TOC distributed platform.
\end{itemize}
}

\vspace{0.25em}

\NewEntry{Yelp}{Software Engineer Intern}{San Francisco, CA}{May 2017 -- Aug 2017}
\Description{
\begin{itemize}
	\item Improved data documentation service and data warehouse reporting as a member of Yelp's Consumer Analytics and Metrics team.
	\item Developed backend infrastructure for collecting, cleaning, and analyzing usage data for Yelp's data warehouse and implemented frontend visualizations to describe and convey information to data warehouse administrators.
	\item Provided insight into how Yelp engineers query the data warehouse, guiding decisions to improve system performance.
	\item Redesigned React user interface for data documentation service in order to improve developer workflow.
\end{itemize}
}

\vspace{0.25em}

\NewEntry{Cornell Database Group, Data Vocalization Project}{Research Assistant}{Ithaca, NY}{Jan 2017 -- May 2018}
\Description{
\begin{itemize}
\item Research optimization problem of how to efficiently represent relational data through audio interfaces by applying data mining algorithms to translate data into natural language speech.
\item Collaborate with Professor Immanuel Trummer to develop a database system funded by a Google Faculty Research Award.
\item Implemented and refined exhaustive and polynomial time approximation algorithms that translate datasets into speech output. These algorithms minimize speaking time subject to user-defined precision constraints.
\end{itemize}
}

\vspace{0.25em}

\NewEntry{Cornell University Computer Science Dept.}{Teaching Assistant, Database Systems}{Ithaca, NY}{Aug 2016 -- Dec 2018}
\Description{
\begin{itemize}
\item Conducted weekly office hours, created and updated problem sets and solutions, and graded problem sets for Database Systems course.
\item Developed automated grading scripts used by team of 20 teaching assistants to optimize grading processes.
\end{itemize}
}

\vspace{0.25em}

\NewEntry{Toast}
{Software Engineer Intern}{Boston, MA}{Jun 2016 -- Aug 2016}
\Description{
\begin{itemize}
\item Improved database layer of Toast's core web application by refactoring the way developers write and release changes to data sources, increasing the reliability of deploying database schema migrations in both development and production environments and improving the efficiency of the engineering team.
\item Presented new development workflow to 40+ member engineering team and developed tooling and documentation to facilitate the transition to the new schema migration process.
\end{itemize}
}
